---
title: "CoralTypePrediction"
author: "Eva Kovacs"
date: "18/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## packages

```{r what you need }
install.packages("tidyverse")
install.packages("janitor")
install.packages("skimr")
install.packages("stringr")
install.packages("data.table")
install.packages("ggthemes")
install.packages("RColorBrewer")
install.packages("gmodels")
install.packages("dplyr")
install.packages("plyr")
install.packages("foreign")
##install.packages('Rtools')
##install.packages('jwbannister/seepsVeg')


library(tidyverse) # use install.packages("tidyverse") if receive an error message
library(janitor) # use install.packages("janitor") if receive an error message
library(skimr)  # use install.packages("skimr") if receive an error message
library(stringr) # use install.packages("stringr") if receive an error message
library(data.table)
library(ggthemes)
library(RColorBrewer)
library(gmodels)
library(dplyr)
library(plyr)
library(foreign)
##library(Rtools)
##library(jwbannister/seepsVeg)

```


# Set the number of significant digits to preserve

```{r}

# Set
options(digits = 10)

#Check
options()

```

# Read in Files

```{r}
# Import file fom folder

head(CCMR_pred)

#  X1 Longitude Latitude pred.Bra pred.Mass pred.Plat
#  <dbl>     <dbl>    <dbl>    <dbl>     <dbl>     <dbl>
#1     1      146.    -17.8     36.2      64.4      5.06
```

# Rescale the values for each coral type (0-100)

```{r}
# Makea copy
CCMR <- CCMR_pred

# Change all negative prediction values to zero

setDT(CCMR)
for(j in grep('^pred', names(CCMR))){
 set(CCMR, i= which(CCMR[[j]]<0), j= j, value=0)
}

## Re-scale

# Calculate the SUM of the predicted coral types

CCMR<- CCMR%>%
  rowwise()%>%
  mutate(sum = sum(pred.Bra, pred.Mass, pred.Plat))

remove(CCMR_pred)

# Rescale the values

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(Bra0100 = (100*(pred.Bra/sum)))

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(Mass0100 = (100*(pred.Mass/sum)))

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(Plat0100 = (100*(pred.Plat/sum)))

CCMR<- CCMR%>%
  rowwise()%>%
  mutate(sum2 = sum(Bra0100, Mass0100, Plat0100))

max(CCMR$sum2)
min(CCMR$sum2)

# Write to file

CCMRScaled <- write.csv(CCMR, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/CCMRScaled.csv")

```

# Calculate Dominant Coral Form (5%)

```{r 5% domiance}
CCMR <- CCMRScaled

CCMR <- mutate(CCMR, B = Bra0100)
CCMR <- mutate(CCMR, M = Mass0100)
CCMR <- mutate(CCMR, P = Plat0100)

#copy
CCMR2 <- CCMR

# recall
CCMR <- CCMR2

# calculate 5% dominance
CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy5 = fifelse((((B - M) >= 5) & ((B - P) >= 5)), "Branching", 
                          fifelse((((M - B) >= 5) & ((M - P) >= 5)), "Massive",
                         fifelse((((P - B) >=5) & ((P - M) >=5)), "Plate",
         
                         fifelse(((B <5) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <5) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <5) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy5)


# Write to file

#RC_Mitch <- write.csv(RC_Mitch, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/Output/RC_Heron2018_DomBen.csv")


```

# 15% Dominance

```{r 15% dominance}

#copy
CCMR3 <- CCMR

# recall
CCMR <- CCMR3

# calculate 15% dominance
CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy15 = fifelse((((B - M) >= 15) & ((B - P) >= 15)), "Branching", 
                          fifelse((((M - B) >= 15) & ((M - P) >= 15)), "Massive",
                         fifelse((((P - B) >=15) & ((P - M) >=15)), "Plate",
         
                         fifelse(((B <15) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <15) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <15) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy15)


```

# Just plain dominant

```{r Dominant by value}

#copy
CCMR4 <- CCMR

# recall
CCMR <- CCMR4

# calculate 15% dominance
CCMR <- CCMR%>%
  rowwise()%>%
  mutate(Dominant = fifelse(((B > M) & (B > P)), "Branching",
                            fifelse(((M > B)  & (M > P)), "Massive",
                                     fifelse(((P > B) & (P > M)), "Plate","None"))))

unique(CCMR$Dominant)

```

# Tidy and save

```{r select rows and save}

# select rows
CCMR <- CCMR %>%
  select("X1", "Longitude", "Latitude", "B":"Dominant")

# Write to csv
CCMR <- write.csv(CCMR, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/Output/CoralTypeMapping/CCMR_CT.csv")

```
# ##################
# ################## 
# Validation Points

# To extract any val points from the training points

```{r find the val points!}

####### To extract validation points
CCMR_Waves_val<- mutate(CCMR_Waves_val, Latitude=P_Lat)
CCMR_Waves_val<- mutate(CCMR_Waves_val, Longitude=P_Long)

CCMR_Val <- CCMR_Waves_val%>%
  select("Latitude":"Longitude")

# try to extract predictions for the val points 
# This shouldn't work as they weren't used for the modeling
# But some are pairing so delete those points

#CCMR_Valpreds <- merge(CCMR_Val, CCMR_simple, by=c("Longitude","Latitude"),all.x=TRUE, all.y=FALSE) 

CCMR_Valpreds <- left_join(CCMR_Val, CCMR_simple, by =c( "Longitude", "Latitude"))

# No CCMR val are joining - Yay

#######

```

# Create dominance for Validation

```{r Dominance val points}

CCMR_Waves_val <- mutate(CCMR_Waves_val, B = BrPerTot)
CCMR_Waves_val <- mutate(CCMR_Waves_val, M = MaPerTot)
CCMR_Waves_val <- mutate(CCMR_Waves_val, P = PPerTot)

#copy
CCMR <- CCMR_Waves_val%>%
  select("PeriPt", "Latitude":"P")

```

# Calculate Dominances

```{r 5%}

# calculate 5% dominance

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy5 = fifelse((((B - M) >= 5) & ((B - P) >= 5)), "Branching", 
                          fifelse((((M - B) >= 5) & ((M - P) >= 5)), "Massive",
                         fifelse((((P - B) >=5) & ((P - M) >=5)), "Plate",
         
                         fifelse(((B <5) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <5) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <5) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy5)
```


```{r 15%}

# calculate 15% dominance

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy15 = fifelse((((B - M) >= 15) & ((B - P) >= 15)), "Branching", 
                          fifelse((((M - B) >= 15) & ((M - P) >= 15)), "Massive",
                         fifelse((((P - B) >=15) & ((P - M) >=15)), "Plate",
         
                         fifelse(((B <15) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <15) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <15) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy15)
```


```{r 30%}

# calculate 30% dominance

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy30 = fifelse((((B - M) >= 30) & ((B - P) >= 30)), "Branching", 
                          fifelse((((M - B) >= 30) & ((M - P) >= 30)), "Massive",
                         fifelse((((P - B) >=30) & ((P - M) >=30)), "Plate",
         
                         fifelse(((B <30) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <30) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <30) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy30)
```

# Save

```{r}
CCMR <- write.csv(CCMR, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/Validation/CCMR_ValPts20210202.csv")
```

#Read in large DBF

```{r}

setwd("//sees-rsrc//Data/3DGBR_HabMap/Modelling/GEE_Output/Pixels_0-11")


# load the dbfs
dbf_paths <- list.files("CCMRCCMR25to10_cliptoSRSRS.dbf", full.names = T)
dbf_regions <- unlist(lapply(list.files("CCMR25to10_cliptoSRSRS.dbf"), function(x) strsplit(x, "_")[[1]][1]))
names(dbf_paths) <- dbf_regions
dbf_dfs <- mapply(load_dbf, dbf_paths, dbf_regions, SIMPLIFY = F)
dbf_dfs <- lapply(dbf_dfs, na.omit)

# alternate

CCMR <- read.dbf(system.file("CCMRCCMR25to10_cliptoSRSRS.dbf", package="foreign")[1])
str(x)
summary(x)


```

# Determine difference between CoralNet and ReefCLoud for CCMR

```{r}

# CoralNet CCMR output

CCMRct <- CCMR_Kalinda_Fleur_BENTHIC_DATA_submit_v2

CCMRtype <-
  CCMRct %>%
  rowwise()%>%
  mutate(
    Branching = (ACR_BRA + ACR_BRA_B_ + ACR_HIP + ACR_HIP_B_ + BRA_OTH + BRA_OTH_B_ +POCI+ POCI_B_ +POR_BRA+ POR_BRA_B_),
    Plate = (ACR_PE + ACR_PE_B_+ BRA_TAB_Ac+ BRA_TAB_B_ + TFP_RDG_Al +TFP_RDG_B_ +TFP_RND_Al +TFP_RND_B_),
    Massive = (BRA_DIG_Ac+ BRA_DIG_B_ +FAV_MUS +FAV_MUS_B_ +MASE_OTH +MASEoth_B_ + POR_ENC + POR_ENC_B_ + POR_MASS + POR_MAS_B_),
    Mixed = (ACR_OTH +ACR_OTH_B_+ OTH_HC+ OTH_HC_B_))

### For CR's kneejerk comparison
CCMRtype <- mutate(CCMRtype, Name = image_name)

summary_inference_2020June06_NoDups <- mutate(summary_inference_2020June06_NoDups, Name = image_name)

ReefCloud <- summary_inference_2020June06_NoDups %>%
  inner_join(CCMRtype, by = "Name")

# write file
 ReefCloud <- write.csv(ReefCloud, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/ReefCloudCCMR.csv")


#####
CCMRtype2 <-
  CCMRtype%>%
  select("Name", "Latitude", "Longitude", "Branching", "Massive", "Plate","Mixed")

print(count(CCMRtype2$Mixed))
print(count(CCMRtype2$Massive))
print(count(CCMRtype2$Branching))
print(count(CCMRtype2$Plate))

#CNb <- ggplot(CCMRtype2, aes(x=Branching)+
#                geom_histogram)

# ReefCloud CCMR output


CCMRrct <-summary_inference_2020June06_NoDups%>%
  select("image_name", "Branching","Massive","Plate")

CCMRrct <- mutate(CCMRrct, Name=image_name)
CCMRrct <-CCMRrct%>%
  select("Name", "Branching","Massive","Plate")
CCMRrct <- mutate(CCMRrct, BR=Branching)
CCMRrct <- mutate(CCMRrct, MA=Massive)
CCMRrct <- mutate(CCMRrct, PL=Plate)

CCMRrct <-CCMRrct%>%
  select("Name", "BR","MA","PL")

print(count(CCMRrct$Mixed))
print(count(CCMRrct$Massive))
print(count(CCMRrct$Branching))
print(count(CCMRrct$Plate))

ReefCloud <- CCMRrct
CoralNet <- CCMRtype2
# Compare the two outputs

Compare <- inner_join(ReefCloud, CoralNet, by = "Name")

# write file
 Compare <- write.csv(Compare, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/AnnotatonComparison.csv")

#facet_wrap(Zone~., nc=2)+
```

# Plot frequencies

```{r}

# ReefCloud
rcb <- hist(Compare$BR, main = "", xlab = "ReefCloud Branching")
rcm <- hist(Compare$MA, main = "", xlab = "ReefCloud Massive")
rcp <- hist(Compare$PL, main = "", xlab = "ReefCloud Plate")

# CoralNet
cnb <- hist(Compare$Branching, main = "", xlab = "CoralNet Branching")
cnm <- hist(Compare$Massive, main = "", xlab = "CoralNet Massive")
cnp <- hist(Compare$Plate, main = "", xlab = "CoralNet Plate")
cnx <- hist(Compare$Mixed, main = "", xlab = "CoralNet Mixed")

rm(CCMR_Kalinda_Fleur_BENTHIC_DATA_submit_v2)
rm(CCMRrct)
rm(CCMRctype)
rm(CCMRtype2)
rm(Compare)
rm(CoralNet)
rm(cnb)
rm(cnm)
rm(cnp)
rm(cnx)
rm(summary_inference_2020June06_NoDups)
rm(ReefCloud)
rm(rcb)
rm(rcm)
rm(rcp)

```

# ###########################################################
# Sort out CoralNet data for Mitch (coordinates and groupings)
# #############################################################

# SGBR June
```{r}
# Southern GBR June
# Copy data
SGBRJune <- X201906_SGBR

# Group data according to spreadsheet - Coral Type
SGBRJunetype <-
  SGBRJune %>%
  rowwise()%>%
  mutate( 
    Branching = (`ACR-BRA` + `ACR-BRA-B` + `ACR-HIP` + `ACR-HIP-B` + `BRA_OTH` + `BRA_OTH-B` + `POCI` + `POCI-B` + `POR-BRA` + `POR-BRA-B`),
    Plate = (`ACR-PE` + `ACR-PE-B` + `BRA_TAB-Ac` + `BRA_TAB-B` + `TFP_RDG_Al` + `TFP_RDG-B` + `TFP_RND_Al` + `TFP_RND-B`),
    Massive = (`BRA_DIG_Ac` + `BRA_DIG_B` + `FAV-MUS` + `FAV-MUS-B` + `MASE_OTH` + `MASEoth-B` + `POR-ENC` + `POR-ENC-B` + `POR-MASS` + `POR-MAS-B`),
    Mixed = (`ACR-OTH` + `ACR-OTH-B` + `OTH-HC` + `OTH-HC-B`),
    CT_Oth = (`ALC-SF` + `ALC-SF-B` + `GORG`  + `GORG-B` + `MINV_COTS` + `MOB-INV` + `OTH-SF` + `OTH-SF-B` + `OTH-SINV` + `Sand` + `Other` + `TAPE` + `Unc` + `Unk` + `WATE` + `ALG_OTH` + `BMA_sand` + `CAL_CCA_DC` + `CAL_CCA_RB` + `Caul` + `Chlor` + `Cya_spe` + `Dicsp` + `EAM_DHC` + `EAM_RB` + `Lobph` + `MACR_Cal_H` + `MAECBS` + `Pad` + `Turbin` + `Seagrass`))
    
SGBRJunetype <-
  SGBRJunetype %>%
  rowwise()%>%
  mutate( 
    CT_Tot = (`Branching` + `Massive` + `Plate` + `Mixed` + `CT_Oth`)) 

colnames(SGBRJunetype)
unique(SGBRJunetype$CT_Tot)

# Group according to Benthic Type
SGBRJunetype <-
  SGBRJunetype %>%
  rowwise()%>%
  mutate( 
    HC = (`ACR-BRA` + `ACR-BRA-B` + `ACR-HIP` + `ACR-HIP-B` + `BRA_OTH` + `BRA_OTH-B` + `POCI` + `POCI-B` + `POR-BRA` + `POR-BRA-B` + `ACR-PE` + `ACR-PE-B` + `BRA_TAB-Ac` + `BRA_TAB-B` + `TFP_RDG_Al` + `TFP_RDG-B` + `TFP_RND_Al` + `TFP_RND-B` + `BRA_DIG_Ac` + `BRA_DIG_B` + `FAV-MUS` + `FAV-MUS-B` + `MASE_OTH` + `MASEoth-B` + `POR-ENC` + `POR-ENC-B` + `POR-MASS` + `POR-MAS-B` + `ACR-OTH` + `ACR-OTH-B` + `OTH-HC` + `OTH-HC-B`),
    SC = (`ALC-SF` + `ALC-SF-B` + `GORG`  + `GORG-B` + `OTH-SF` + `OTH-SF-B`),
    SD = (`Sand` + `BMA_sand`),
    RB = (`CAL_CCA_RB` + `EAM_RB`),
    RK = (`CAL_CCA_DC` + `EAM_DHC`),
    AL = (`ALG_OTH` + `Caul` + `Chlor` + `Cya_spe` + `Dicsp` +  `Lobph` + `MACR_Cal_H` + `MAECBS` + `Pad` + `Turbin`),
    OT = (`MINV_COTS` + `MOB-INV`  + `OTH-SINV` + `Other` + `TAPE` + `Unc` + `Unk` + `WATE`),
    SG = (`Seagrass`))
    
SGBRJunetype <-
  SGBRJunetype %>%
  rowwise()%>%
  mutate( 
    Ben_Tot = (`HC` + `SC` + `SD` + `RB` + `RK` + `AL` + `OT` + `SG`)) 

colnames(SGBRJunetype)
unique(SGBRJunetype$Ben_Tot)

# CLip the columns

SGBRJune_Mitch <- SGBRJunetype %>%
  select("Name", "Branching":"Ben_Tot")

# Add coordinates

SGBRJune_MitchCoords <- SGBRJune_Mitch%>%
  left_join(SGBR_transects2, by ="Name")

SGBRJune_MitchCoords <- SGBRJune_MitchCoords%>%
  select("Name", "Longitude","Latitude", "Branching":"Ben_Tot")

# write file
 SGBRJune_MitchCoords <- write.csv(SGBRJune_MitchCoords, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Mitch2021/SGBR201906.csv")

```

# SGBR ALL

```{r Southern GBR ALL}
# Southern GBR ALL
# Read in data

# Group data according to spreadsheet - Coral Type
SGBRtype <-
  SGBRallwithCoords %>%
  rowwise()%>%
  mutate( 
    Branching = (`ACR-BRA` + `ACR-BRA-B` + `ACR-HIP` + `ACR-HIP-B` + `BRA_OTH` + `BRA_OTH-B` + `POCI` + `POCI-B` + `POR-BRA` + `POR-BRA-B`),
    Plate = (`ACR-PE` + `ACR-PE-B` + `BRA_TAB-Ac` + `BRA_TAB-B` + `TFP_RDG_Al` + `TFP_RDG-B` + `TFP_RND_Al` + `TFP_RND-B`),
    Massive = (`BRA_DIG_Ac` + `BRA_DIG_B` + `FAV-MUS` + `FAV-MUS-B` + `MASE_OTH` + `MASEoth-B` + `POR-ENC` + `POR-ENC-B` + `POR-MASS` + `POR-MAS-B`),
    Mixed = (`ACR-OTH` + `ACR-OTH-B` + `OTH-HC` + `OTH-HC-B`),
    CT_Oth = (`ALC-SF` + `ALC-SF-B` + `GORG`  + `GORG-B` + `MINV_COTS` + `MOB-INV` + `OTH-SF` + `OTH-SF-B` + `OTH-SINV` + `Sand` + `Other` + `TAPE` + `Unc` + `Unk` + `WATE` + `ALG_OTH` + `BMA_sand` + `CAL_CCA_DC` + `CAL_CCA_RB` + `Caul` + `Chlor` + `Cya_spe` + `Dicsp` + `EAM_DHC` + `EAM_RB` + `Lobph` + `MACR_Cal_H` + `MAECBS` + `Pad` + `Turbin` + `Seagrass`))
    
SGBRtype <-
  SGBRtype %>%
  rowwise()%>%
  mutate( 
    CT_Tot = (`Branching` + `Massive` + `Plate` + `Mixed` + `CT_Oth`)) 

colnames(SGBRtype)
unique(SGBRtype$CT_Tot)

# Group according to Benthic Type
SGBRtype <-
  SGBRtype %>%
  rowwise()%>%
  mutate( 
    HC = (`ACR-BRA` + `ACR-BRA-B` + `ACR-HIP` + `ACR-HIP-B` + `BRA_OTH` + `BRA_OTH-B` + `POCI` + `POCI-B` + `POR-BRA` + `POR-BRA-B` + `ACR-PE` + `ACR-PE-B` + `BRA_TAB-Ac` + `BRA_TAB-B` + `TFP_RDG_Al` + `TFP_RDG-B` + `TFP_RND_Al` + `TFP_RND-B` + `BRA_DIG_Ac` + `BRA_DIG_B` + `FAV-MUS` + `FAV-MUS-B` + `MASE_OTH` + `MASEoth-B` + `POR-ENC` + `POR-ENC-B` + `POR-MASS` + `POR-MAS-B` + `ACR-OTH` + `ACR-OTH-B` + `OTH-HC` + `OTH-HC-B`),
    SC = (`ALC-SF` + `ALC-SF-B` + `GORG`  + `GORG-B` + `OTH-SF` + `OTH-SF-B`),
    SD = (`Sand` + `BMA_sand`),
    RB = (`CAL_CCA_RB` + `EAM_RB`),
    RK = (`CAL_CCA_DC` + `EAM_DHC`),
    AL = (`ALG_OTH` + `Caul` + `Chlor` + `Cya_spe` + `Dicsp` +  `Lobph` + `MACR_Cal_H` + `MAECBS` + `Pad` + `Turbin`),
    OT = (`MINV_COTS` + `MOB-INV`  + `OTH-SINV` + `Other` + `TAPE` + `Unc` + `Unk` + `WATE`),
    SG = (`Seagrass`))
    
SGBRtype <-
  SGBRtype %>%
  rowwise()%>%
  mutate( 
    Ben_Tot = (`HC` + `SC` + `SD` + `RB` + `RK` + `AL` + `OT` + `SG`)) 

colnames(SGBRtype)
unique(SGBRtype$Ben_Tot)

# CLip the columns

SGBR_Mitch <- SGBRtype %>%
  select("Name", "Longitude","Latitude", "Branching":"Ben_Tot")

# write file
 SGBR_Mitch <- write.csv(SGBR_Mitch, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Mitch2021/SGBRall_CT_ben.csv")

```

# CCMR

```{r}
# CCMR 
# add coordinates to Legacy
Legacy <- inner_join(percent_covers_Legacy,LegacyCoordinates, by ="Name")

# bind CCMR and Legacy
CCMRleg <- bind_rows(CCMR_Kalinda_Fleur_BENTHIC_DATA_submit_v2, Legacy)

# Copy data
CCMRct <- CCMRleg

CCMRtype <-
  CCMRct %>%
  rowwise()%>%
  mutate(
    Branching = (ACR_BRA + ACR_BRA_B_ + ACR_HIP + ACR_HIP_B_ + BRA_OTH + BRA_OTH_B_ +POCI+ POCI_B_ +POR_BRA+ POR_BRA_B_),
    Plate = (ACR_PE + ACR_PE_B_+ BRA_TAB_Ac+ BRA_TAB_B_ + TFP_RDG_Al +TFP_RDG_B_ +TFP_RND_Al +TFP_RND_B_),
    Massive = (BRA_DIG_Ac+ BRA_DIG_B_ +FAV_MUS +FAV_MUS_B_ +MASE_OTH +MASEoth_B_ + POR_ENC + POR_ENC_B_ + POR_MASS + POR_MAS_B_),
    Mixed = (ACR_OTH +ACR_OTH_B_+ OTH_HC+ OTH_HC_B_), 
    CT_Oth = (ALC_SF + ALC_SF_B_ + GORG  + GORG_B_ + MINV_COTS + MOB_INV + OTH_SF + OTH_SF_B_ + OTH_SINV + Sand + Other + F_TAPE + Unc + Unk + WATE + ALG_OTH + BMA_sand + CAL_CCA_DC + CAL_CCA_RB + Caul + Chlor + Cya_spe + Dicsp + EAM_DHC + EAM_RB + Lobph + MACR_Cal_H + MAECBS + Pad + Turbin + Seagrass))
    
CCMRtype <-
  CCMRtype %>%
  rowwise()%>%
  mutate( 
    CT_Tot = (`Branching` + `Massive` + `Plate` + `Mixed` + `CT_Oth`)) 

colnames(CCMRtype)
unique(CCMRtype$CT_Tot)

# Group according to Benthic Type
CCMRtype <-
  CCMRtype %>%
  rowwise()%>%
  mutate( 
    HC = (ACR_BRA + ACR_BRA_B_ + ACR_HIP + ACR_HIP_B_ + BRA_OTH + BRA_OTH_B_ +POCI+ POCI_B_ +POR_BRA+ POR_BRA_B_ + ACR_PE + ACR_PE_B_+ BRA_TAB_Ac+ BRA_TAB_B_ + TFP_RDG_Al +TFP_RDG_B_ +TFP_RND_Al +TFP_RND_B_ + BRA_DIG_Ac+ BRA_DIG_B_ +FAV_MUS +FAV_MUS_B_ +MASE_OTH +MASEoth_B_ + POR_ENC + POR_ENC_B_ + POR_MASS + POR_MAS_B_ + ACR_OTH +ACR_OTH_B_+ OTH_HC+ OTH_HC_B_),
    SC = (ALC_SF + ALC_SF_B_ + GORG  + GORG_B_  + OTH_SF + OTH_SF_B_),
    SD = (Sand + BMA_sand),
    RB = (CAL_CCA_RB + EAM_RB),
    RK = (CAL_CCA_DC + EAM_DHC),
    AL = (ALG_OTH + Caul + Chlor + Cya_spe + Dicsp +  Lobph + MACR_Cal_H + MAECBS + Pad + Turbin),
    OT = (MINV_COTS + MOB_INV  + OTH_SINV + Other + F_TAPE + Unc + Unk + WATE),
    SG = (Seagrass))
    
CCMRtype <-
  CCMRtype %>%
  rowwise()%>%
  mutate( 
    Ben_Tot = (`HC` + `SC` + `SD` + `RB` + `RK` + `AL` + `OT` + `SG`)) 

colnames(CCMRtype)
unique(CCMRtype$Ben_Tot)

# Select columns

CCMR_Mitch <- CCMRtype %>%
  select("Name", "Latitude":"Ben_Tot")

# write file
 CCMR_Mitch <- write.csv(CCMR_Mitch, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Mitch2021/CCMRall_CT_ben.csv")

```

# FNGBR

```{r FNGBR}
# FNGBR
# Read in data

# Group data according to spreadsheet - Coral Type
FNGBRtype <-
  FNGBRwithCoords %>%
  rowwise()%>%
  mutate( 
    Branching = (`ACR-BRA` + `ACR-BRA-B` + `ACR-HIP` + `ACR-HIP-B` + `BRA_OTH` + `BRA_OTH-B` + `POCI` + `POCI-B` + `POR-BRA` + `POR-BRA-B`),
    Plate = (`ACR-PE` + `ACR-PE-B` + `BRA_TAB-Ac` + `BRA_TAB-B` + `TFP_RDG_Al` + `TFP_RDG-B` + `TFP_RND_Al` + `TFP_RND-B`),
    Massive = (`BRA_DIG_Ac` + `BRA_DIG_B` + `FAV-MUS` + `FAV-MUS-B` + `MASE_OTH` + `MASEoth-B` + `POR-ENC` + `POR-ENC-B` + `POR-MASS` + `POR-MAS-B`),
    Mixed = (`ACR-OTH` + `ACR-OTH-B` + `OTH-HC` + `OTH-HC-B`),
    CT_Oth = (`ALC-SF` + `ALC-SF-B` + `GORG`  + `GORG-B` + `MINV_COTS` + `MOB-INV` + `OTH-SF` + `OTH-SF-B` + `OTH-SINV` + `Sand` + `Other` + `TAPE` + `Unc` + `Unk` + `WATE` + `ALG_OTH` + `BMA_sand` + `CAL_CCA_DC` + `CAL_CCA_RB` + `Caul` + `Chlor` + `Cya_spe` + `Dicsp` + `EAM_DHC` + `EAM_RB` + `Lobph` + `MACR_Cal_H` + `MAECBS` + `Pad` + `Turbin` + `Seagrass`))
    
FNGBRtype <-
  FNGBRtype %>%
  rowwise()%>%
  mutate( 
    CT_Tot = (`Branching` + `Massive` + `Plate` + `Mixed` + `CT_Oth`)) 

colnames(FNGBRtype)
unique(FNGBRtype$CT_Tot)

# Group according to Benthic Type
FNGBRtype <-
  FNGBRtype %>%
  rowwise()%>%
  mutate( 
    HC = (`ACR-BRA` + `ACR-BRA-B` + `ACR-HIP` + `ACR-HIP-B` + `BRA_OTH` + `BRA_OTH-B` + `POCI` + `POCI-B` + `POR-BRA` + `POR-BRA-B` + `ACR-PE` + `ACR-PE-B` + `BRA_TAB-Ac` + `BRA_TAB-B` + `TFP_RDG_Al` + `TFP_RDG-B` + `TFP_RND_Al` + `TFP_RND-B` + `BRA_DIG_Ac` + `BRA_DIG_B` + `FAV-MUS` + `FAV-MUS-B` + `MASE_OTH` + `MASEoth-B` + `POR-ENC` + `POR-ENC-B` + `POR-MASS` + `POR-MAS-B` + `ACR-OTH` + `ACR-OTH-B` + `OTH-HC` + `OTH-HC-B`),
    SC = (`ALC-SF` + `ALC-SF-B` + `GORG`  + `GORG-B` + `OTH-SF` + `OTH-SF-B`),
    SD = (`Sand` + `BMA_sand`),
    RB = (`CAL_CCA_RB` + `EAM_RB`),
    RK = (`CAL_CCA_DC` + `EAM_DHC`),
    AL = (`ALG_OTH` + `Caul` + `Chlor` + `Cya_spe` + `Dicsp` +  `Lobph` + `MACR_Cal_H` + `MAECBS` + `Pad` + `Turbin`),
    OT = (`MINV_COTS` + `MOB-INV`  + `OTH-SINV` + `Other` + `TAPE` + `Unc` + `Unk` + `WATE`),
    SG = (`Seagrass`))
    
FNGBRtype <-
  FNGBRtype %>%
  rowwise()%>%
  mutate( 
    Ben_Tot = (`HC` + `SC` + `SD` + `RB` + `RK` + `AL` + `OT` + `SG`)) 

colnames(FNGBRtype)
unique(FNGBRtype$Ben_Tot)

# CLip the columns

FNGBR_Mitch <- FNGBRtype %>%
  select("Name", "Longitude","Latitude", "Branching":"Ben_Tot")

# write file
 FNGBR_Mitch <- write.csv(FNGBR_Mitch, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Mitch2021/FNGBR_CT_ben.csv")

```

# ########################################################
# ########################################################
# Group data according to peripoint and summarise coral type for WGBR

```{r Peripoint to each image}

# WGBR

# Join datframes by "Name"

WGBR_CT <- inner_join(WholeGBR_images, WGBR_Th_FD_P_20190525, by = "Name")

# write to csv

#FNGBR_CT <- write.csv(FNGBR_CT, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/Output/JC/CT_total/FNGBR_PPts.csv")


```

# Summarise by PeriPoint

```{r Summarise by PeriPt}

# Count number of occurrences of each PeriPt and add that to the table

WGBR_PPt <- WGBR_CT %>%
  group_by(PeriPt)%>%
  dplyr::mutate(count = n())

colnames(WGBR_PPt)

WGBR_PPt <- select(WGBR_PPt, "Name":"Longitude", "Branching":"count")

# Summarise by PeriPt

# Calculate Total coral type points per zone
# when in doubt, add dplyr::

WGBR_TotPts <- WGBR_PPt %>%
  select("Name":"Longitude", "Branching":"CT_Oth" ,"PeriPt": "count")%>%
  dplyr::group_by(PeriPt)%>%
  dplyr::mutate(TotPts = count*100, TotBrpts = sum(Branching), TotMapts = sum(Massive), TotPpts = sum(Plate),  TotMix = sum(Mixed), TotOthPts = sum(CT_Oth))

colnames(WGBR_TotPts)

# Calculate fractional amount of coral types

WGBR_TotPts <- dplyr::mutate(WGBR_TotPts, BoverTot = (TotBrpts/TotPts), MoverTot = (TotMapts/TotPts), PoverTot = (TotPpts/TotPts), MixoverTot = (TotMix/TotPts))

colnames(WGBR_TotPts)

# Determine Dominant Coral Type per zone

WGBR_DomPerZone <- mutate(WGBR_TotPts, DomZone = ifelse((BoverTot == 0) & (MoverTot == 0) & (PoverTot == 0) & (MixoverTot == 0), "None",
                                                           ifelse(((BoverTot) > (MoverTot)) & ((BoverTot) > (PoverTot)) & ((BoverTot) > (MixoverTot)),  "Branching",                                               
        ifelse(((MoverTot) > (BoverTot)) & ((MoverTot) > (PoverTot)) & ((MoverTot) > (MixoverTot)), "Massive", 
               ifelse(((PoverTot) > (BoverTot)) & ((PoverTot) > (MoverTot)) & ((PoverTot) > (MixoverTot)), "Plate", 
                      "Mixed")))))

unique(WGBR_DomPerZone$DomZone)

head(WGBR_DomPerZone)

colnames(WGBR_DomPerZone)

# write to file

WGBR_DomPerZone <- write.csv(WGBR_DomPerZone, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Mitch2021/WGBR_DomPerZone20210326.csv")


```

# Calculate percentage for dominant coral based on count per zone

```{r}

WGBRZone <- WGBR_DomPerZone20210326
colnames(WGBRZone)

# remove duplicated PeriPt rows
WGBRZone <- WGBRZone %>% distinct(PeriPt, .keep_all = TRUE)

# No Scaling ###################################

# Dominant CT by percentage with 5% difference

WGBRZone <- mutate(WGBRZone, DomByPer5 = if_else((BoverTot == 0) & (MoverTot == 0) & (PoverTot == 0) & (MixoverTot == 0), "None",
                                                      if_else(((MoverTot - BoverTot) >=0.05) & ((MoverTot - PoverTot) >= 0.05) & ((MoverTot - MixoverTot) >= 0.05), "Massive",
                                                      if_else(((BoverTot - MoverTot) >=0.05) & ((BoverTot - PoverTot) >=0.05) & ((BoverTot - MixoverTot) >=0.05), "Branching",
                                                              if_else(((PoverTot - BoverTot) >=0.05) & ((PoverTot - MoverTot) >=0.05) & ((PoverTot - MixoverTot) >=0.05), "Plate", 
                                                                      if_else((BoverTot <0.05) & (MoverTot == 0) & (PoverTot == 0) & (MixoverTot == 0), "Branching",
                                                                              if_else((MoverTot < 0.0005) & (BoverTot == 0) & (PoverTot == 0) & (MixoverTot == 0), "Massive",
                                                                                      if_else((PoverTot < 0.0005) & (MoverTot == 0) & (BoverTot ==0) & (MixoverTot == 0), "Plate",
                                                                                              "Mixed"))))))))

unique(WGBRZone$DomByPer5)

# Dominant CT by percentage with 15% difference

WGBRZone <- mutate(WGBRZone, DomByPer15 = if_else((BoverTot == 0) & (MoverTot == 0) & (PoverTot == 0) & (MixoverTot == 0), "None",
                                                      if_else(((MoverTot - BoverTot) >=0.15) & ((MoverTot - PoverTot) >= 0.15) & ((MoverTot - MixoverTot) >= 0.15), "Massive",
                                                      if_else(((BoverTot - MoverTot) >=0.15) & ((BoverTot - PoverTot) >=0.15) & ((BoverTot - MixoverTot) >=0.15), "Branching",
                                                              if_else(((PoverTot - BoverTot) >=0.15) & ((PoverTot - MoverTot) >=0.15) & ((PoverTot - MixoverTot) >=0.15), "Plate", 
                                                                      if_else((BoverTot <0.15) & (MoverTot == 0) & (PoverTot == 0) & (MixoverTot == 0), "Branching",
                                                                              if_else((MoverTot < 0.0005) & (BoverTot == 0) & (PoverTot == 0) & (MixoverTot == 0), "Massive",
                                                                                      if_else((PoverTot < 0.0005) & (MoverTot == 0) & (BoverTot ==0) & (MixoverTot == 0), "Plate",
                                                                                              "Mixed"))))))))

unique(WGBRZone$DomByPer15)

WGBRZone <- select(WGBRZone, "Name", "PeriPt":"P_Long", "Branching":"CT_Oth", "count":"DomByPer15")

# write to file

WGBRZone <- write.csv(WGBRZone, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Mitch2021/WGBRDomCTbyPercentage20210326.csv")



```



# Haven't used yet##########################
# Determine Percentages of Coral, Algae, unconsolidated, consolidated

```{r percentages and scaling factor}
# Percentages of Coral, Algae, unconsolidated, consolidated

colnames(WGBR_DomPerZone)

FNGBR_Scaling <- mutate(FNGBR_DomPerZoneB, C_Pts = TotBrpts + TotMapts + TotPpts, Con_Pts = TotRKPts + TotRPts)

colnames(FNGBR_Scaling)
head(FNGBR_Scaling)

FNGBR_Scaling <- mutate(FNGBR_Scaling, C_Per = 100*(C_Pts/TotPts), Con_Per = 100*(Con_Pts/TotPts), Alg_Per = 100*(TotAlgPts/TotPts), Uncon_Per = 100*(TotSandPts/TotPts), OT_Per = 100*(TotOthPts/TotPts))

FNGBR_Scaling <- mutate(FNGBR_Scaling, TotPer = C_Per + Con_Per + Alg_Per + Uncon_Per + OT_Per)

unique(FNGBR_Scaling$TotPer)

FNGBR_Scaling <- mutate(FNGBR_Scaling, Scale_F = 100/C_Per)

unique(FNGBR_Scaling$Scale_F)

# write to csv

FNGBR_Scaling <- write.csv(FNGBR_Scaling, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/PeripointArcData/FNQ/CTworking/FNGBR_Scaling.csv")

```

# Determine coral type percentages and subsequently dominant coral type per zone by percentage

```{r coral type % and dom CT/zone}

FNGBR_DomSF <- FNGBR_Scaling

FNGBR_DomSF <- mutate(FNGBR_DomSF, BrPerTot = ifelse(Scale_F > 0, 100*(BoverTot*Scale_F), "NA"))

FNGBR_DomSF <- mutate(FNGBR_DomSF, MaPerTot = ifelse(Scale_F > 0, 100*(MoverTot*Scale_F), "NA"))

FNGBR_DomSF <- mutate(FNGBR_DomSF, PPerTot = ifelse(Scale_F > 0, 100*(PoverTot*Scale_F), "NA"))

FNGBR_DomSF <- mutate(FNGBR_DomSF, CTPerTot = BrPerTot + MaPerTot + PPerTot)

unique(FNGBR_DomSF$CTPerTot)

# Dominant CT by Percentage

FNGBR_DomSF <- mutate(FNGBR_DomSF, DomByPer = if_else((BrPerTot == 0) & (MaPerTot == 0) & (PPerTot == 0), "None",
                                                      if_else((MaPerTot > BrPerTot) & (MaPerTot > PPerTot), "Massive",
                                                      if_else((BrPerTot > MaPerTot) & (BrPerTot > PPerTot), "Branching",
                                                              if_else((PPerTot > BrPerTot) & (PPerTot > MaPerTot), "Plate", "Mixed")))))

unique(FNGBR_DomSF$DomByPer)

# Dominant CT by percentage with 5% difference

FNGBR_DomSF <- mutate(FNGBR_DomSF, DomByPer5 = if_else((BrPerTot == 0) & (MaPerTot == 0) & (PPerTot == 0), "None",
                                                      if_else(((MaPerTot - BrPerTot) >=5) & ((MaPerTot - PPerTot) >= 5), "Massive",
                                                      if_else(((BrPerTot - MaPerTot) >=5) & ((BrPerTot - PPerTot) >=5), "Branching",
                                                              if_else(((PPerTot - BrPerTot) >=5) & ((PPerTot - MaPerTot) >=5), "Plate", 
                                                                      if_else((BrPerTot <5) & (MaPerTot == 0) & ( PPerTot == 0), "Branching",
                                                                              if_else((MaPerTot <5) & (BrPerTot == 0) & (PPerTot == 0), "Massive",
                                                                                      if_else((PPerTot <5) & (MaPerTot == 0) & (BrPerTot ==0), "Plate",
                                                                                              "Mixed"))))))))

unique(FNGBR_DomSF$DomByPer5)

# Dominant CT by percentage with 15% difference

FNGBR_DomSF <- mutate(FNGBR_DomSF, DomByPer15 = if_else((BrPerTot == 0) & (MaPerTot == 0) & (PPerTot == 0), "None",
                                                      if_else(((MaPerTot - BrPerTot) >= 15) & ((MaPerTot - PPerTot) >= 15), "Massive",
                                                      if_else(((BrPerTot - MaPerTot) >=15) & ((BrPerTot - PPerTot) >=15), "Branching",
                                                              if_else(((PPerTot - BrPerTot) >=15) & ((PPerTot - MaPerTot) >=15), "Plate", 
                                                                      if_else((BrPerTot <15) & (MaPerTot == 0) & ( PPerTot == 0), "Branching",
                                                                              if_else((MaPerTot <15) & (BrPerTot == 0) & (PPerTot == 0), "Massive",
                                                                                      if_else((PPerTot <15) & (MaPerTot == 0) & (BrPerTot ==0), "Plate",
                                                                                              "Mixed"))))))))

unique(FNGBR_DomSF$DomByPer15)

colnames(FNGBR_DomSF)

# write to file

FNGBR_DomSF <- write.csv(FNGBR_DomSF, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/PeripointArcData/FNQ/CTworking/FNGBR_DomCTbyPercentage.csv")

```

# Determine dominant substrate per zone and coral point ratios

```{r coral point ratios & Dom substrate/zone}

FNGBR_sub <- select(FNGBR_DomCTbyPercentage, "FID_FNQ_th":"DomByPer15")

# Coral Pt ratios

FNGBR_sub <- mutate(FNGBR_sub, DomCPts = if_else(DomByPer == "Branching", TotBrpts,
                                                 if_else(DomByPer == "Massive", TotMapts, 
                                                         if_else(DomByPer == "Plate", TotPpts, 0))))

unique(FNGBR_sub$DomCPts)

FNGBR_sub <- mutate(FNGBR_sub, DomCToverTotCT = (DomCPts/(TotBrpts + TotMapts + TotPpts)))

FNGBR_sub <- mutate(FNGBR_sub, BroverTotCT = (TotBrpts/(TotBrpts + TotMapts + TotPpts)))

FNGBR_sub <- mutate(FNGBR_sub, MaCToverTotCT = (TotMapts/(TotBrpts + TotMapts + TotPpts)))

FNGBR_sub <- mutate(FNGBR_sub, PCToverTotCT = (TotPpts/(TotBrpts + TotMapts + TotPpts)))

# Determine dominant substrate

FNGBR_sub <- mutate(FNGBR_sub, DomSub = if_else(Con_Pts > TotSandPts, "Consolidated",
                                                if_else(TotSandPts > Con_Pts, "Unconsolidated", "None")))

unique(FNGBR_sub$DomSub)

# write to csv

FNGBR_sub <- write.csv(FNGBR_sub, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/Output/JC/DomPer/FNGBR_DomCT_DomSub.csv")

```

# write file for Dom CT Dom sub

```{r read in data}

FNGBR_DomCT <- FNGBR_DomCT_DomSub

colnames(FNGBR_DomCT)

FNGBR_DomCT_Domsub_JC <- select(FNGBR_DomCT, "PeriPt":"P_Long", "count", "TotPts", "TotBrpts", "BoverTot", "TotMapts", "MoverTot", "TotPpts", "PoverTot", "DomZone", "BrPerTot":"PPerTot", "CTPerTot", "DomByPer", "DomCPts":"PCToverTotCT", "Con_Pts", "TotSandPts", "DomSub")

# write to file

FNGBR_DomCT_Domsub_JC <- write.csv(FNGBR_DomCT_Domsub_JC, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/Output/JC/Finals/FNGBR_DomCT_DomSub20190520.csv")

```

# write file for benthic percentages

```{r read in data}

FNGBR_percentages <- FNGBR_DomCT_DomSub

colnames(FNGBR_percentages)

FNGBR_Per_JC <- select(FNGBR_percentages, "PeriPt":"P_Long", "C_Pts", "Con_Pts", "TotAlgPts", "TotSandPts", "TotOthPts", "C_Per", "Con_Per", "Alg_Per", "Uncon_Per", "OT_Per", "Scale_F")

# write to file

FNGBR_Per_JC <- write.csv(FNGBR_Per_JC, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/Output/JC/Finals/FNGBR_Percentages20190520.csv")

```
