---
title: "WholeGBR"
author: "Eva Kovacs"
date: "01/02/2021"
output: html_document
---

## packages

```{r what you need }
install.packages("tidyverse")
install.packages("janitor")
install.packages("skimr")
install.packages("stringr")
install.packages("data.table")
install.packages("ggthemes")
install.packages("RColorBrewer")
install.packages("gmodels")
install.packages("dplyr")
install.packages("plyr")


library(tidyverse) # use install.packages("tidyverse") if receive an error message
library(janitor) # use install.packages("janitor") if receive an error message
library(skimr)  # use install.packages("skimr") if receive an error message
library(stringr) # use install.packages("stringr") if receive an error message
library(data.table)
library(ggthemes)
library(RColorBrewer)
library(gmodels)
library(dplyr)
library(plyr)

```


# Set the number of significant digits to preserve

```{r}

# Set
options(digits = 10)

#Check
options()

```

# FNGBR
# Create unique row numbers

```{r Creat unique row numbers}
# Read CSV files from folder

# Append regions
FNGBR_ALL <- dplyr::bind_rows(FNGBR_pred1,FNGBR_pred2)

FNGBR_ALL <- na.omit(FNGBR_ALL)

FNGBR_ALL <- FNGBR_ALL %>% dplyr::mutate(id = row_number())

# Make ID FNGBR specific
FNGBR_ALL <- FNGBR_ALL %>% dplyr::mutate(Region = as.character("FNGBR_"))

FNGBR_ALL <- FNGBR_ALL %>% unite("ID", Region:id, remove = TRUE)

FNGBR <- FNGBR_ALL %>%
  select("ID", "Longitude":"pred.Plat")

# write to CSV

FNGBR <- write.csv(FNGBR, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/FNGBR_ALL_simple.csv")

Far <- FNGBR_ALL_simple

max(Far$pred.Bra)
max(Far$pred.Mass)
max(Far$pred.Plat)

min(Far$pred.Bra)
min(Far$pred.Mass)
min(Far$pred.Plat)

Far %>%
  summarise(
          
          mean_B = mean(pred.Bra, na.rm = TRUE),
          mean_M = mean(pred.Mass, na.rm = TRUE),
          mean_P = mean(pred.Plat, na.rm = TRUE)
          #sd = sd(pred.Bra),
          #sd = sd(pred.Mass),
          #sd = sd(pred.Plat)
          )

```

# ##############
# CCMR
# Create unique row numbers

```{r Creat unique row numbers}
# Read CSV files from folder

# Append regions

CCMR <- na.omit(CCMR_pred)

CCMR <- CCMR %>% dplyr::mutate(id = row_number())

# Make ID CCMR specific
CCMR <- CCMR %>% dplyr::mutate(Region = as.character("CCMR_"))

CCMR <- CCMR %>% unite("ID", Region:id, remove = TRUE)

CCMRa <- CCMR %>%
  select("ID", "pred.Bra":"pred.Plat")

# write to CSV

CCMR <- write.csv(CCMR, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/CCMR_simple.csv")

CC <- CCMRa

max(CC$pred.Bra)
max(CC$pred.Mass)
max(CC$pred.Plat)

min(CC$pred.Bra)
min(CC$pred.Mass)
min(CC$pred.Plat)

CC %>%
  summarise(
          
          #mean_B = mean(pred.Bra, na.rm = TRUE),
          #mean_M = mean(pred.Mass, na.rm = TRUE),
          #mean_P = mean(pred.Plat, na.rm = TRUE),
          sd = sd(pred.Bra),
          sd = sd(pred.Mass),
          sd = sd(pred.Plat)
          )

```
# ##################
# ################## 
# Validation Points

# To extract any val points from the training points

```{r find the val points!}

####### To extract validation points
CCMR_Waves_val<- mutate(CCMR_Waves_val, Latitude=P_Lat)
CCMR_Waves_val<- mutate(CCMR_Waves_val, Longitude=P_Long)

CCMR_Val <- CCMR_Waves_val%>%
  select("Latitude":"Longitude")

# try to extract predictions for the val points 
# This shouldn't work as they weren't used for the modeling
# But some are pairing so delete those points

#CCMR_Valpreds <- merge(CCMR_Val, CCMR_simple, by=c("Longitude","Latitude"),all.x=TRUE, all.y=FALSE) 

CCMR_Valpreds <- left_join(CCMR_Val, CCMR_simple, by =c( "Longitude", "Latitude"))

# No CCMR val are joining - Yay

#######

```

# Create dominance for Validation

```{r Dominance val points}

CCMR_Waves_val <- mutate(CCMR_Waves_val, B = BrPerTot)
CCMR_Waves_val <- mutate(CCMR_Waves_val, M = MaPerTot)
CCMR_Waves_val <- mutate(CCMR_Waves_val, P = PPerTot)

#copy
CCMR <- CCMR_Waves_val%>%
  select("PeriPt", "Latitude":"P")

```

# Calculate Dominances

```{r 5%}

# calculate 5% dominance

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy5 = fifelse((((B - M) >= 5) & ((B - P) >= 5)), "Branching", 
                          fifelse((((M - B) >= 5) & ((M - P) >= 5)), "Massive",
                         fifelse((((P - B) >=5) & ((P - M) >=5)), "Plate",
         
                         fifelse(((B <5) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <5) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <5) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy5)
```


```{r 15%}

# calculate 15% dominance

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy15 = fifelse((((B - M) >= 15) & ((B - P) >= 15)), "Branching", 
                          fifelse((((M - B) >= 15) & ((M - P) >= 15)), "Massive",
                         fifelse((((P - B) >=15) & ((P - M) >=15)), "Plate",
         
                         fifelse(((B <15) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <15) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <15) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy15)
```


```{r 30%}

# calculate 30% dominance

CCMR <- CCMR%>%
  rowwise()%>%
  mutate(DomBy30 = fifelse((((B - M) >= 30) & ((B - P) >= 30)), "Branching", 
                          fifelse((((M - B) >= 30) & ((M - P) >= 30)), "Massive",
                         fifelse((((P - B) >=30) & ((P - M) >=30)), "Plate",
         
                         fifelse(((B <30) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <30) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <30) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(CCMR$DomBy30)
```

# Save

```{r}
CCMR <- write.csv(CCMR, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/Validation/CCMR_ValPts20210202.csv")
```

# ##############
# MKY
# Create unique row numbers

```{r Creat unique row numbers}
# Read CSV files from folder

# Append regions
MKY_ALL <- dplyr::bind_rows(MKY_preda, MKY_predb,MKY_predc,MKY_predd)

MKY_ALL <- na.omit(MKY_ALL)

MKY_ALL <- MKY_ALL %>% dplyr::mutate(id = row_number())

# Make ID MKY specific
MKY_ALL <- MKY_ALL %>% dplyr::mutate(Region = as.character("MKY_"))

MKY_ALL <- MKY_ALL %>% unite("ID", Region:id, remove = TRUE)

MKY <- MKY_ALL %>%
  select("ID", "Longitude":"pred.Plat")

# write to CSV

MKY <- write.csv(MKY, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/MKY_simple.csv")

MKY<- MKY_simple

max(MKY$pred.Bra)
max(MKY$pred.Mass)
max(MKY$pred.Plat)

min(MKY$pred.Bra)
min(MKY$pred.Mass)
min(MKY$pred.Plat)

MKY %>%
  summarise(
          
          mean_B = mean(pred.Bra, na.rm = TRUE),
          mean_M = mean(pred.Mass, na.rm = TRUE),
          mean_P = mean(pred.Plat, na.rm = TRUE),
          sd = sd(pred.Bra),
          sd = sd(pred.Mass),
          sd = sd(pred.Plat)
          )

```

# ##################
# ################## 
# Validation Points

# To extract any val points from the training points

```{r find the val points!}

####### To extract validation points
MKY_Waves_val<- mutate(MKY_Waves_val, Latitude=P_Lat)
MKY_Waves_val<- mutate(MKY_Waves_val, Longitude=P_Long)

MKY_Val <- MKY_Waves_val%>%
  select("PeriPt", "Latitude":"Longitude","BrPerTot":"PPerTot")

# try to extract predictions for the val points 
# This shouldn't work as they weren't used for the modeling
# But some are pairing so delete those points

# return rows from x where there are not matching values in y
MKY_Valpreds <- anti_join(MKY_Val, MKY_simple, by =c( "Longitude", "Latitude"))

#######

```

# Create dominance for Validation

```{r Dominance val points}

MKY_Valpreds <- mutate(MKY_Valpreds, B = BrPerTot)
MKY_Valpreds <- mutate(MKY_Valpreds, M = MaPerTot)
MKY_Valpreds <- mutate(MKY_Valpreds, P = PPerTot)

#copy
MKY <- MKY_Valpreds%>%
  select("PeriPt":"Longitude", "B":"P")

```

# Calculate Dominances

```{r 5%}

# calculate 5% dominance

MKY <- MKY%>%
  rowwise()%>%
  mutate(DomBy5 = fifelse((((B - M) >= 5) & ((B - P) >= 5)), "Branching", 
                          fifelse((((M - B) >= 5) & ((M - P) >= 5)), "Massive",
                         fifelse((((P - B) >=5) & ((P - M) >=5)), "Plate",
         
                         fifelse(((B <5) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <5) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <5) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(MKY$DomBy5)
```


```{r 15%}

# calculate 15% dominance

MKY <- MKY%>%
  rowwise()%>%
  mutate(DomBy15 = fifelse((((B - M) >= 15) & ((B - P) >= 15)), "Branching", 
                          fifelse((((M - B) >= 15) & ((M - P) >= 15)), "Massive",
                         fifelse((((P - B) >=15) & ((P - M) >=15)), "Plate",
         
                         fifelse(((B <15) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <15) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <15) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(MKY$DomBy15)
```


```{r 30%}

# calculate 30% dominance

MKY <- MKY%>%
  rowwise()%>%
  mutate(DomBy30 = fifelse((((B - M) >= 30) & ((B - P) >= 30)), "Branching", 
                          fifelse((((M - B) >= 30) & ((M - P) >= 30)), "Massive",
                         fifelse((((P - B) >=30) & ((P - M) >=30)), "Plate",
         
                         fifelse(((B <30) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <30) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <30) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(MKY$DomBy30)

```

# Save

```{r}
MKY <- write.csv(MKY, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/Validation/ForValidation/MKY_ValPts20210202.csv")
```


# ##############
# TSV
# Create unique row numbers

```{r Creat unique row numbers}
# Read CSV files from folder

# Append regions
TSV_ALL <- dplyr::bind_rows(TSV_predda, TSV_preddb)

TSV_ALL <- na.omit(TSV_ALL)

TSV_ALL <- TSV_ALL %>% dplyr::mutate(id = row_number())

# Make ID TSV specific
TSV_ALL <- TSV_ALL %>% dplyr::mutate(Region = as.character("TSV_"))

TSV_ALL <- TSV_ALL %>% unite("ID", Region:id, remove = TRUE)

TSV <- TSV_ALL %>%
  select("ID", "Longitude":"pred.Plat")

# write to CSV

TSV <- write.csv(TSV, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/TSV_simple.csv")


max(TSV$pred.Bra)
max(TSV$pred.Mass)
max(TSV$pred.Plat)

min(TSV$pred.Bra)
min(TSV$pred.Mass)
min(TSV$pred.Plat)

TSV %>%
  summarise(
          
          #mean_B = mean(pred.Bra, na.rm = TRUE),
          #mean_M = mean(pred.Mass, na.rm = TRUE),
          #mean_P = mean(pred.Plat, na.rm = TRUE),
          sd = sd(pred.Bra),
          sd = sd(pred.Mass),
          sd = sd(pred.Plat)
          )

```


# ##################
# ################## 
# Validation Points

# To extract any val points from the training points

```{r find the val points!}

####### To extract validation points
TSV_Waves_val<- mutate(TSV_Waves_val, Latitude=P_Lat)
TSV_Waves_val<- mutate(TSV_Waves_val, Longitude=P_Long)

TSV_Val <- TSV_Waves_val%>%
  select("PeriPt", "Latitude":"Longitude","BrPerTot":"PPerTot")

# try to extract predictions for the val points 
# This shouldn't work as they weren't used for the modeling
# But some are pairing so delete those points

#TSV_Valpreds <- merge(TSV_Val, TSV_simple, by=c("Longitude","Latitude"),all.x=TRUE, all.y=FALSE) 

# return rows from x where there are not matching values in y
TSV_Valpreds <- anti_join(TSV_Val, TSV_simple, by =c( "Longitude", "Latitude"))

#######

```

# Create dominance for Validation

```{r Dominance val points}

TSV_Valpreds <- mutate(TSV_Valpreds, B = BrPerTot)
TSV_Valpreds <- mutate(TSV_Valpreds, M = MaPerTot)
TSV_Valpreds <- mutate(TSV_Valpreds, P = PPerTot)

#copy
TSV <- TSV_Valpreds%>%
  select("PeriPt":"Longitude", "B":"P")

```

# Calculate Dominances

```{r 5%}

# calculate 5% dominance

TSV <- TSV%>%
  rowwise()%>%
  mutate(DomBy5 = fifelse((((B - M) >= 5) & ((B - P) >= 5)), "Branching", 
                          fifelse((((M - B) >= 5) & ((M - P) >= 5)), "Massive",
                         fifelse((((P - B) >=5) & ((P - M) >=5)), "Plate",
         
                         fifelse(((B <5) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <5) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <5) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(TSV$DomBy5)
```


```{r 15%}

# calculate 15% dominance

TSV <- TSV%>%
  rowwise()%>%
  mutate(DomBy15 = fifelse((((B - M) >= 15) & ((B - P) >= 15)), "Branching", 
                          fifelse((((M - B) >= 15) & ((M - P) >= 15)), "Massive",
                         fifelse((((P - B) >=15) & ((P - M) >=15)), "Plate",
         
                         fifelse(((B <15) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <15) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <15) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(TSV$DomBy15)
```


```{r 30%}

# calculate 30% dominance

TSV <- TSV%>%
  rowwise()%>%
  mutate(DomBy30 = fifelse((((B - M) >= 30) & ((B - P) >= 30)), "Branching", 
                          fifelse((((M - B) >= 30) & ((M - P) >= 30)), "Massive",
                         fifelse((((P - B) >=30) & ((P - M) >=30)), "Plate",
         
                         fifelse(((B <30) & (M == 0) & (P == 0)), "Branching",
                         fifelse(((M <30) & (B == 0) & (P == 0)), "Massive",
                         fifelse(((P <30) & (M == 0) & (B == 0)), "Plate", "Mixed")))))))
                         

unique(TSV$DomBy30)

```

# Save

```{r}
TSV <- write.csv(TSV, file = "C:/Users/uqekovac/Documents/R/Coding/GBRBenthic2020/CoralTypeMapping/Wave_Predictions_per_region/Validation/ForValidation/TSV_ValPts20210202.csv")
```

